CODECHECK: an Open Science initiative for the independent execution of computations underlying research articles during peer review to improve reproducibility

### 2021-06-16 reviews/response-round1.md

We have written a detailed 'response to reviewers' document which is
available at
<https://github.com/codecheckers/paper/blob/master/reviews/response-round1.md>

However, in brief, we have added text to the manuscript, to the "related work", "limitations" and "future work" to address key issues made by the reviewers and by one public comment.  These edits have resulted in a few additional sentences in our article; no changes to figures/tables or references were required.

Furthermore, we noticed an inconsistent use of the terms "workflow" and "process", and decided to use "CODECHECK workflow", "computational workflow", and "publication/review process" more consistently in the revision of the manuscript.

We have used a macro, \rev{...} to record our edits in this revision.  If you wish to see the edits in italics, please change the definition in the preamable of the latex file.

@@

# Response to reviewers

We thank the reviewers for their comments on our manuscript.  Key comments, requiring responses, are below, quoted, followed by our answers.  (We have added numbers to the key points.)
